---
title: "mini_project2_code"
author: "Luna Bellitto, Isabella Mullen, Nina Rice, Asad Tariq"
output: pdf_document
date: "2025-05-23"
---

## Loading Libraries

```{r}
library(dplyr)
library(tidyverse)
library(glmnet)
library(randomForest)
library(ggplot2)
library(corrplot)
library(RColorBrewer)
library(gridExtra)
library(huxtable)
library(caret)
```


## Reading the Dataset

```{r}
df <- read_csv("../data/mini_project2_data/Data_Carrardetal2022MedTeach.csv", show_col_types = FALSE)
str(df)
```


## Check for missing data

```{r}
# Count of missing values per column
colSums(is.na(df))
```

## Renaming the columns for readability

```{r}
df <- df %>% 
  dplyr::rename(
    job_satisfaction = jspe,
    cog_empathy = qcae_cog,
    aff_empathy = qcae_aff,
    academic_motivation = amsp,
    empathy_mean = erec_mean,
    depression = cesd,
    anxiety = stai_t,
    burnout_exhaustion = mbi_ex,
    burnout_cynicism = mbi_cy,
    burnout_efficacy = mbi_ea
  )
```

## Correlation Plot

```{r, fig.height=6, fig.width=8}
c<-cor(df)
corrplot(c, method = "number",type = "upper",number.cex = 0.6,
         tl.cex = 0.7,mar = c(1,1,1,1), col = brewer.pal(n = 8, name = "RdBu"))
```

We see that `depression`, `anxiety`, `burnout_exhaustion`, `burnout_cynicism`, and `burnout_efficacy` are highly correlated.

```{r, fig.height=6, fig.width=8}
c<-cor(df[, 16:20])
corrplot(c, method = "number",type = "upper",number.cex = 0.6,
         tl.cex = 0.7,mar = c(1,1,1,1), col = brewer.pal(n = 8, name = "RdBu"))
```

## Remove unwanted columns from the dataset

```{r}
# Removing the id column
df <- subset(df, select = -id) 
df
```

## Reverse-coding and Standardizing

```{r}
# Reverse-code professional efficacy
max_burnout_efficacy <- max(df$burnout_efficacy, na.rm = TRUE)
df$burnout_efficacy_rev <- max_burnout_efficacy - df$burnout_efficacy

# Create a combined burnout score

# Z-score standardization
df$burnout_exhaustion_z <- scale(df$burnout_exhaustion)
df$burnout_cynicism_z <- scale(df$burnout_cynicism)
df$burnout_efficacy_rev_z <- scale(df$burnout_efficacy_rev)

df
```

## Constructing subsets for each burnout score

```{r}
df_features <- subset(df, select = c(age, year, sex, glang, part, job,
                                       stud_h, health, psyt, job_satisfaction,
                                       cog_empathy, aff_empathy,
                                       academic_motivation,empathy_mean,
                                       depression, anxiety))

df_exhaustion <- cbind(df_features, burnout_exhaustion_z = df$burnout_exhaustion_z)
df_cynicism <- cbind(df_features, burnout_cynicism_z = df$burnout_cynicism_z)
df_efficacy <- cbind(df_features, burnout_efficacy_rev_z = df$burnout_efficacy_rev_z)
df_all_burnout <- cbind(df_features, burnout_total = df$burnout_exhaustion_z + df$burnout_cynicism_z + df$burnout_efficacy_rev_z)
```

## Fitting Random Forest for each target variable

```{r, fig.width=8, fig.height=5}
# Fit Random Forest regression model
set.seed(123)
rf_exhaustion <- randomForest(
  burnout_exhaustion_z ~ ., 
  data = df_exhaustion,
  importance = TRUE,
  ntree = 500
)

# Print model summary
print(rf_exhaustion)

# Plot variable importance
varImpPlot(rf_exhaustion, type = 1, main = "Random Forest Variable Importance (MSE Increase)")
```


```{r}
# Extract and rank variable importance
ex_importance_df <- importance(rf_exhaustion, type = 1)  # %IncMSE
ex_importance_df <- data.frame(Variable = rownames(ex_importance_df), IncMSE = ex_importance_df[, 1])
ex_importance_df <- ex_importance_df[order(-ex_importance_df$IncMSE), ]
```

```{r, fig.width=8, fig.height=6}
set.seed(123)

# Splitting df_exhaustion
df_ex_split <- createDataPartition(df_exhaustion$burnout_exhaustion_z, p = 0.7, list = FALSE)
df_ex_train <- df_exhaustion[df_ex_split, ]
df_ex_test <- df_exhaustion[-df_ex_split, ]

# Get ordered list of all variables based on importance
all_vars <- ex_importance_df$Variable

# Create empty vector to store MSPEs
ex_mspe_values <- numeric(length(all_vars))

# Loop over 1 to total number of variables
for (k in 1:length(all_vars)) {
  # Select top k variables
  selected_vars <- all_vars[1:k]
  
  # Create formula
  formula_k <- as.formula(paste("burnout_exhaustion_z ~", paste(selected_vars, collapse = " + ")))
  
  # Fit Random Forest model on training data
  rf_k <- randomForest(
    formula_k,
    data = df_ex_train,
    ntree = 500
  )
  
  # Predict on test data
  preds_k <- predict(rf_k, newdata = df_ex_test)
  
  # Compute MSPE
  ex_mspe_values[k] <- mean((preds_k - df_ex_test$burnout_exhaustion_z)^2)
}

# Create data frame for plotting
ex_mspe_plot_df <- data.frame(
  Num_Variables = 1:length(all_vars),
  MSPE = ex_mspe_values
)

# Find optimal number of variables (index with lowest MSPE)
ex_optimal_k <- which.min(ex_mspe_plot_df$MSPE)
ex_optimal_mspe <- ex_mspe_plot_df$MSPE[ex_optimal_k]

cat("Optimal number of top variables:", ex_optimal_k, "\n")
cat("Corresponding MSPE:", round(ex_optimal_mspe, 4), "\n")

ggplot(ex_mspe_plot_df, aes(x = Num_Variables, y = MSPE)) +
  geom_line(color = "steelblue", size = 1.2) +
  geom_point(color = "red", size = 2) +
  geom_vline(xintercept = ex_optimal_k, linetype = "dashed", color = "darkgreen") +
  geom_text(data = data.frame(x = ex_optimal_k, y = ex_optimal_mspe + 0.05),
          aes(x = x, y = y, label = paste0("Optimal = ", ex_optimal_k)),
          inherit.aes = FALSE,
          vjust = 0, hjust = 0.5,
          color = "darkgreen", fontface = "bold") +
  labs(
    title = "MSPE vs. Number of Top Variables (Burnout-Exhaustion Random Forest)",
    x = "Number of Top Variables",
    y = "Mean Squared Prediction Error"
  ) +
  theme_minimal()
```


```{r, fig.width=8, fig.height=5}
# Fit Random Forest regression model
set.seed(123)
rf_cynicism <- randomForest(
  burnout_cynicism_z ~ ., 
  data = df_cynicism,
  importance = TRUE,
  ntree = 500
)

# Print model summary
print(rf_cynicism)

# Plot variable importance
varImpPlot(rf_cynicism, type = 1, main = "Random Forest Variable Importance (MSE Increase)")
```

```{r}
# Extract and rank variable importance
cy_importance_df <- importance(rf_cynicism, type = 1)  # %IncMSE
cy_importance_df <- data.frame(Variable = rownames(cy_importance_df), IncMSE = cy_importance_df[, 1])
cy_importance_df <- cy_importance_df[order(-cy_importance_df$IncMSE), ]

# Show top predictors
cy_importance_df  # Top 10 for review
```

```{r, fig.width=8, fig.height=6}
set.seed(123)

# Splitting df_exhaustion
df_cy_split <- createDataPartition(df_cynicism$burnout_cynicism_z, p = 0.7, list = FALSE)
df_cy_train <- df_cynicism[df_cy_split, ]
df_cy_test <- df_cynicism[-df_cy_split, ]

# Get ordered list of all variables based on importance
all_vars <- cy_importance_df$Variable

# Create empty vector to store MSPEs
cy_mspe_values <- numeric(length(all_vars))

# Loop over 1 to total number of variables
for (k in 1:length(all_vars)) {
  # Select top k variables
  selected_vars <- all_vars[1:k]
  
  # Create formula
  formula_k <- as.formula(paste("burnout_cynicism_z ~", paste(selected_vars, collapse = " + ")))
  
  # Fit Random Forest model on training data
  rf_k <- randomForest(
    formula_k,
    data = df_cy_train,
    ntree = 500
  )
  
  # Predict on test data
  preds_k <- predict(rf_k, newdata = df_cy_test)
  
  # Compute MSPE
  cy_mspe_values[k] <- mean((preds_k - df_cy_test$burnout_cynicism_z)^2)
}

# Create data frame for plotting
cy_mspe_plot_df <- data.frame(
  Num_Variables = 1:length(all_vars),
  MSPE = cy_mspe_values
)

# Find optimal number of variables (index with lowest MSPE)
cy_optimal_k <- which.min(cy_mspe_plot_df$MSPE)
cy_optimal_mspe <- cy_mspe_plot_df$MSPE[cy_optimal_k]

cat("Optimal number of top variables:", cy_optimal_k, "\n")
cat("Corresponding MSPE:", round(cy_optimal_mspe, 4), "\n")

ggplot(cy_mspe_plot_df, aes(x = Num_Variables, y = MSPE)) +
  geom_line(color = "steelblue", size = 1.2) +
  geom_point(color = "red", size = 2) +
  geom_vline(xintercept = cy_optimal_k, linetype = "dashed", color = "darkgreen") +
  geom_text(data = data.frame(x = cy_optimal_k, y = cy_optimal_mspe + 0.05),
          aes(x = x, y = y, label = paste0("Optimal = ", cy_optimal_k)),
          inherit.aes = FALSE,
          vjust = 0, hjust = 0.5,
          color = "darkgreen", fontface = "bold") +
  labs(
    title = "MSPE vs. Number of Top Variables (Burnout-Cynicism Random Forest)",
    x = "Number of Top Variables",
    y = "Mean Squared Prediction Error"
  ) +
  theme_minimal()
```


```{r, fig.width=8, fig.height=5}
# Fit Random Forest regression model
set.seed(123)
rf_efficacy <- randomForest(
  burnout_efficacy_rev_z ~ ., 
  data = df_efficacy,
  importance = TRUE,
  ntree = 500
)

# Print model summary
print(rf_efficacy)

# Plot variable importance
varImpPlot(rf_efficacy, type = 1, main = "Random Forest Variable Importance (MSE Increase)")
```

```{r}
# Extract and rank variable importance
ea_importance_df <- importance(rf_efficacy, type = 1)  # %IncMSE
ea_importance_df <- data.frame(Variable = rownames(ea_importance_df), IncMSE = ea_importance_df[, 1])
ea_importance_df <- ea_importance_df[order(-ea_importance_df$IncMSE), ]

# Show top predictors
ea_importance_df  # Top 10 for review
```


```{r, fig.width=8, fig.height=6}
set.seed(123)

# Splitting df_exhaustion
df_ea_split <- createDataPartition(df_efficacy$burnout_efficacy_rev_z, p = 0.7, list = FALSE)
df_ea_train <- df_efficacy[df_ea_split, ]
df_ea_test <- df_efficacy[-df_ea_split, ]

# Get ordered list of all variables based on importance
all_vars <- ea_importance_df$Variable

# Create empty vector to store MSPEs
ea_mspe_values <- numeric(length(all_vars))

# Loop over 1 to total number of variables
for (k in 1:length(all_vars)) {
  # Select top k variables
  selected_vars <- all_vars[1:k]
  
  # Create formula
  formula_k <- as.formula(paste("burnout_efficacy_rev_z ~", paste(selected_vars, collapse = " + ")))
  
  # Fit Random Forest model on training data
  rf_k <- randomForest(
    formula_k,
    data = df_ea_train,
    ntree = 500
  )
  
  # Predict on test data
  preds_k <- predict(rf_k, newdata = df_ea_test)
  
  # Compute MSPE
  ea_mspe_values[k] <- mean((preds_k - df_ea_test$burnout_efficacy_rev_z)^2)
}

# Create data frame for plotting
ea_mspe_plot_df <- data.frame(
  Num_Variables = 1:length(all_vars),
  MSPE = ea_mspe_values
)

# Find optimal number of variables (index with lowest MSPE)
ea_optimal_k <- which.min(ea_mspe_plot_df$MSPE)
ea_optimal_mspe <- ea_mspe_plot_df$MSPE[ea_optimal_k]

cat("Optimal number of top variables:", ea_optimal_k, "\n")
cat("Corresponding MSPE:", round(ea_optimal_mspe, 4), "\n")

ggplot(ea_mspe_plot_df, aes(x = Num_Variables, y = MSPE)) +
  geom_line(color = "steelblue", size = 1.2) +
  geom_point(color = "red", size = 2) +
  geom_vline(xintercept = ea_optimal_k, linetype = "dashed", color = "darkgreen") +
  geom_text(data = data.frame(x = ea_optimal_k, y = ea_optimal_mspe + 0.05),
          aes(x = x, y = y, label = paste0("Optimal = ", ea_optimal_k)),
          inherit.aes = FALSE,
          vjust = 0, hjust = 0.5,
          color = "darkgreen", fontface = "bold") +
  labs(
    title = "MSPE vs. Number of Top Variables (Burnout-Efficacy Random Forest)",
    x = "Number of Top Variables",
    y = "Mean Squared Prediction Error"
  ) +
  theme_minimal()
```

```{r, fig.width=8, fig.height=5}
# Fit Random Forest regression model
set.seed(123)
rf_total_burnout <- randomForest(
  burnout_total ~ ., 
  data = df_all_burnout,
  importance = TRUE,
  ntree = 500
)

# Print model summary
print(rf_total_burnout)

# Plot variable importance
varImpPlot(rf_total_burnout, type = 1, main = "Random Forest Variable Importance (MSE Increase)")
```

```{r}
# Extract and rank variable importance
total_importance_df <- importance(rf_total_burnout, type = 1)  # %IncMSE
total_importance_df <- data.frame(Variable = rownames(total_importance_df), IncMSE = total_importance_df[, 1])
total_importance_df <- total_importance_df[order(-total_importance_df$IncMSE), ]

# Show top predictors
total_importance_df  # Top 10 for review
```

```{r, fig.width=8, fig.height=6}
set.seed(123)

# Splitting df_exhaustion
df_total_split <- createDataPartition(df_all_burnout$burnout_total, p = 0.7, list = FALSE)
df_total_train <- df_all_burnout[df_total_split, ]
df_total_test <- df_all_burnout[-df_total_split, ]

# Get ordered list of all variables based on importance
all_vars <- total_importance_df$Variable

# Create empty vector to store MSPEs
total_mspe_values <- numeric(length(all_vars))

# Loop over 1 to total number of variables
for (k in 1:length(all_vars)) {
  # Select top k variables
  selected_vars <- all_vars[1:k]
  
  # Create formula
  formula_k <- as.formula(paste("burnout_total ~", paste(selected_vars, collapse = " + ")))
  
  # Fit Random Forest model on training data
  rf_k <- randomForest(
    formula_k,
    data = df_total_train,
    ntree = 500
  )
  
  # Predict on test data
  preds_k <- predict(rf_k, newdata = df_total_test)
  
  # Compute MSPE
  total_mspe_values[k] <- mean((preds_k - df_total_test$burnout_total)^2)
}

# Create data frame for plotting
total_mspe_plot_df <- data.frame(
  Num_Variables = 1:length(all_vars),
  MSPE = total_mspe_values
)

# Find optimal number of variables (index with lowest MSPE)
total_optimal_k <- which.min(total_mspe_plot_df$MSPE)
total_optimal_mspe <- total_mspe_plot_df$MSPE[total_optimal_k]

cat("Optimal number of top variables:", total_optimal_k, "\n")
cat("Corresponding MSPE:", round(total_optimal_mspe, 4), "\n")

ggplot(total_mspe_plot_df, aes(x = Num_Variables, y = MSPE)) +
  geom_line(color = "steelblue", size = 1.2) +
  geom_point(color = "red", size = 2) +
  geom_vline(xintercept = total_optimal_k, linetype = "dashed", color = "darkgreen") +
  geom_text(data = data.frame(x = total_optimal_k, y = total_optimal_mspe + 0.05),
          aes(x = x, y = y, label = paste0("Optimal = ", total_optimal_k)),
          inherit.aes = FALSE,
          vjust = 0, hjust = 0.5,
          color = "darkgreen", fontface = "bold") +
  labs(
    title = "MSPE vs. Number of Top Variables (Total-Burnout Random Forest)",
    x = "Number of Top Variables",
    y = "Mean Squared Prediction Error"
  ) +
  theme_minimal()
```

```{r}
ex_importance_df$model = "RF-Exhaustion"
cy_importance_df$model = "RF-Cynicism"
ea_importance_df$model = "RF-Efficacy"
total_importance_df$model = "RF-Total-Burnout"

combined_importance_df <- bind_rows(ex_importance_df, cy_importance_df, ea_importance_df, total_importance_df)
```

## Feature Importance Plot for Random Forests

```{r, fig.width=8, fig.height=10}
ggplot(combined_importance_df, aes(x = reorder(Variable, IncMSE), y = IncMSE, fill = model)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +
  labs(title = "Variable Importance by Model",
       x = "Variable",
       y = "Importance (IncMSE)") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set1")
```

## Plotting MSPE

```{r}
mspe_summary_df <- data.frame(
  Model = rep(c("Exhaustion", "Cynicism", "Efficacy", "Total Burnout"), each = 2),
  Version = rep(c("Full", "Optimal"), times = 4),
  MSPE = c(
    ex_mspe_values[length(ex_mspe_values)], ex_optimal_mspe,
    cy_mspe_values[length(cy_mspe_values)], cy_optimal_mspe,
    ea_mspe_values[length(ea_mspe_values)], ea_optimal_mspe,
    total_mspe_values[length(total_mspe_values)], total_optimal_mspe
  ),
  Optimal_K = c(NA, ex_optimal_k, NA, cy_optimal_k, NA, ea_optimal_k, NA, total_optimal_k)
)
mspe_summary_df$Label <- paste(mspe_summary_df$Model, "(", mspe_summary_df$Version, ")", sep = "")
```


```{r, fig.width=8, fig.height=8}

ggplot(mspe_summary_df, aes(x = Label, y = MSPE, color = Model)) +
  geom_point(size = 4) +

  # Annotate MSPE
  geom_text(aes(label = round(MSPE, 2)), 
            vjust = -1, size = 3.5, color = "black") +

  # Annotate optimal K below Optimal only
  geom_text(
    data = subset(mspe_summary_df, Version == "Optimal"),
    aes(label = paste0("K = ", Optimal_K)),
    vjust = 2, size = 3.3, color = "black", fontface = "italic"
  ) +

  labs(
    title = "MSPE for Full vs Optimal Random Forest Models",
    subtitle = "Each model appears twice (Full and Optimal). K shown only for Optimal.",
    x = "Model Version",
    y = "Mean Squared Prediction Error"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  )
```


## Additional Data Exploration

## Data Exploration

```{r, fig.width=8, fig.height=6}
# Convert sex into a factor to do divide the colors 
x <- as.factor(df$sex)

eff.anx <- ggplot(df, aes(x = anxiety, y = burnout_efficacy_rev_z, color = x)) + geom_point() + 
  scale_color_manual(values = c("2" = "pink", "1" = "blue")) + 
  geom_smooth(method = lm, 
              se = FALSE) + 
  xlab("Anxiety") +
  ylab("Efficacy")


eff.dep <- ggplot(df, aes(x = depression, y = burnout_efficacy_rev_z, color = x)) + geom_point() + 
  scale_color_manual(values = c("2" = "pink", "1" = "blue")) + 
  geom_smooth(method = lm, 
              se = FALSE) + 
  xlab("Depression") +
  ylab("Efficacy")


grid.arrange(eff.anx, eff.dep, ncol=2)
```

```{r, fig.width=8, fig.height=6}
cyn.qnx <- ggplot(df, aes(x = anxiety, y = burnout_cynicism_z, color = x)) + geom_point() + 
  scale_color_manual(values = c("2" = "pink", "1" = "blue")) + 
  geom_smooth(method = lm, 
              se = FALSE) + 
  xlab("Anxiety") +
  ylab("Cynicism")

cyn.dep <- ggplot(df, aes(x = depression, y = burnout_cynicism_z, color = x)) + geom_point() + 
  scale_color_manual(values = c("2" = "pink", "1" = "blue")) + 
  geom_smooth(method = lm, 
              se = FALSE) + 
  xlab("Depression") +
  ylab("Cynicism")


grid.arrange(cyn.qnx, cyn.dep, ncol=2)
```

```{r, fig.width=8, fig.height=6}
exh.qnx <- ggplot(df, aes(x = anxiety, y = burnout_exhaustion_z, color = x)) + geom_point() + 
  scale_color_manual(values = c("2" = "pink", "1" = "blue")) + 
  geom_smooth(method = lm, 
              se = FALSE) + 
  xlab("Anxiety") +
  ylab("Exhaustion")

exh.dep <- ggplot(df, aes(x = depression, y = burnout_exhaustion_z, color = x)) + geom_point() + 
  scale_color_manual(values = c("2" = "pink", "1" = "blue")) + 
  geom_smooth(method = lm, 
              se = FALSE) + 
  xlab("Depression") +
  ylab("Exhaustion")

grid.arrange(exh.qnx, exh.dep, ncol=2)
```

```{r, fig.width=8, fig.height=6}
total_burnout.qnx <- ggplot(df, aes(x = anxiety, y = burnout_efficacy_rev_z + burnout_cynicism_z + burnout_exhaustion_z, color = x)) + geom_point() + 
  scale_color_manual(values = c("2" = "pink", "1" = "blue")) + 
  geom_smooth(method = lm, 
              se = FALSE) + 
  xlab("Anxiety") +
  ylab("Total Burnout")

total_burnout.dep <- ggplot(df, aes(x = depression, y = burnout_efficacy_rev_z + burnout_cynicism_z + burnout_exhaustion_z, color = x)) + geom_point() + 
  scale_color_manual(values = c("2" = "pink", "1" = "blue")) + 
  geom_smooth(method = lm, 
              se = FALSE) + 
  xlab("Depression") +
  ylab("Total Burnout")


grid.arrange(total_burnout.qnx, total_burnout.dep, ncol=2)
```

### Impact of year on burnout

```{r, fig.width=6, fig.height=5}
summary_df_efficacy <- df %>%
  group_by(year) %>%
  summarise(
    mean    = mean(burnout_efficacy_rev_z),
    se      = sd(burnout_efficacy_rev_z) / sqrt(n()),
    lower   = mean - qt(0.975, df = n() - 1) * se,
    upper   = mean + qt(0.975, df = n() - 1) * se
  )

ggplot(summary_df_efficacy, aes(x = year, y = mean)) +
  geom_line() +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  labs(
    x = "Years of Study",
    y = "Mean Efficacy",
    title = "Mean Burnout Efficacy by Year with 95% CI"
  ) +
  theme_minimal()
```

```{r, fig.width=6, fig.height=5}
summary_df_cynicism <- df %>%
  group_by(year) %>%
  summarise(
    mean    = mean(burnout_cynicism_z),
    se      = sd(burnout_cynicism_z) / sqrt(n()),
    lower   = mean - qt(0.975, df = n() - 1) * se,
    upper   = mean + qt(0.975, df = n() - 1) * se
  )

ggplot(summary_df_cynicism, aes(x = year, y = mean)) +
  geom_line() +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  labs(
    x = "Years of Study",
    y = "Mean Cynicism",
    title = "Mean Burnout Cynicism by Year with 95% CI"
  ) +
  theme_minimal()
```

```{r, fig.width=6, fig.height=5}
summary_df_exhaustion <- df %>%
  group_by(year) %>%
  summarise(
    mean    = mean(burnout_exhaustion_z),
    se      = sd(burnout_exhaustion_z) / sqrt(n()),
    lower   = mean - qt(0.975, df = n() - 1) * se,
    upper   = mean + qt(0.975, df = n() - 1) * se
  )

ggplot(summary_df_exhaustion, aes(x = year, y = mean)) +
  geom_line() +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  labs(
    x = "Years of Study",
    y = "Mean Exhaustion",
    title = "Mean Burnout Exhaustion by Year with 95% CI"
  ) +
  theme_minimal()
```

```{r, fig.width=6, fig.height=5}
summary_df_total_burnout <- df %>%
  group_by(year) %>%
  summarise(
    mean    = mean(burnout_efficacy_rev_z + burnout_cynicism_z + burnout_exhaustion_z),
    se      = sd(burnout_efficacy_rev_z + burnout_cynicism_z + burnout_exhaustion_z) / sqrt(n()),
    lower   = mean - qt(0.975, df = n() - 1) * se,
    upper   = mean + qt(0.975, df = n() - 1) * se
  )

ggplot(summary_df_total_burnout, aes(x = year, y = mean)) +
  geom_line() +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  labs(
    x = "Years of Study",
    y = "Mean Total Burnout",
    title = "Mean Total Burnout by Year with 95% CI"
  ) +
  theme_minimal()
```

## Partnership Influence over Mental Health

```{r, fig.width=6}
df$part<-as.factor(df$part)

ggplot(df, aes(x = health, fill = part)) +
  geom_density(alpha=0.7)+
  labs(title='Health by Partership')+
  scale_fill_discrete(labels=c('alone', 'partner'))
```


```{r}
ggplot(df, aes(x = burnout_efficacy_rev_z + burnout_cynicism_z + burnout_exhaustion_z, fill = part)) +
  geom_density(alpha=0.7)+
  labs(title='Total Burnout by Partership')+
  scale_fill_discrete(labels=c('alone', 'partner'))
```


```{r}
ggplot(df, aes(x = anxiety, fill = part)) +
  geom_density(alpha=0.7)+
  labs(title='Anxiety by Partership')+
  scale_fill_discrete(labels=c('alone', 'partner'))
```