---
title: "mini_project2_code"
author: "Luna Bellitto, Isabella Mullen, Nina Rice, Asad Tariq"
date: "2025-05-23"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

## Loading Libraries

```{r}
library(dplyr)
library(tidyverse)
library(glmnet)
library(randomForest)
library(ggplot2)
library(corrplot)
library(RColorBrewer)
library(gridExtra)
library(huxtable)
library(caret)
library(VIM)
```


## Reading the Dataset

```{r}
df <- read_csv("../data/mini_project2_data/Data_Carrardetal2022MedTeach.csv", show_col_types = FALSE)
str(df)
```


## Check for missing data

```{r}
# Count of missing values per column
colSums(is.na(df))

# Visualization of missing data 
dt_miss <- df

a <- aggr(dt_miss, plot = FALSE)
plot(a, numbers = TRUE, prop = FALSE, cex.axis = 0.6, cex.lab = 0.6)
```

## Renaming the columns for readability

```{r}
df <- df %>% 
  dplyr::rename(
    job_satisfaction = jspe,
    cog_empathy = qcae_cog,
    aff_empathy = qcae_aff,
    academic_motivation = amsp,
    empathy_mean = erec_mean,
    depression = cesd,
    anxiety = stai_t,
    burnout_exhaustion = mbi_ex,
    burnout_cynicism = mbi_cy,
    burnout_efficacy = mbi_ea
  )
```

## Correlation Plot

```{r, fig.height=6, fig.width=8}
c<-cor(df)
corrplot(c, method = "number",type = "upper",number.cex = 0.6,
         tl.cex = 0.7,mar = c(1,1,1,1), col = brewer.pal(n = 8, name = "RdBu"))
```

We see that `depression`, `anxiety`, `burnout_exhaustion`, `burnout_cynicism`, and `burnout_efficacy` are highly correlated.

```{r, fig.height=6, fig.width=8}
c<-cor(df[, 16:20])
corrplot(c, method = "number",type = "upper",number.cex = 0.6,
         tl.cex = 0.7,mar = c(1,1,1,1), col = brewer.pal(n = 8, name = "RdBu"))
```

## Remove unwanted columns from the dataset

```{r}
# Removing the id column
df <- subset(df, select = -id) 
df
```

## Reverse-coding and Standardizing

```{r}
# Reverse-code professional efficacy
max_burnout_efficacy <- max(df$burnout_efficacy, na.rm = TRUE)
df$burnout_efficacy_rev <- max_burnout_efficacy - df$burnout_efficacy

# Create a combined burnout score

# Z-score standardization
df$burnout_exhaustion_z <- scale(df$burnout_exhaustion)
df$burnout_cynicism_z <- scale(df$burnout_cynicism)
df$burnout_efficacy_rev_z <- scale(df$burnout_efficacy_rev)

df
```

## Additional Data Exploration

```{r, fig.width=8, fig.height=6}
# # Convert sex into a factor to do divide the colors

df$sex <- as.factor(df$sex)

eff.anx <- ggplot(df, aes(x = anxiety, y = burnout_efficacy_rev_z, color = sex)) + geom_point() + 
  scale_color_manual(values = c("2" = "pink", "1" = "blue")) + 
  geom_smooth(method = lm, 
              se = FALSE) + 
  xlab("Anxiety") +
  ylab("Efficacy")


eff.dep <- ggplot(df, aes(x = depression, y = burnout_efficacy_rev_z, color = sex)) + geom_point() + 
  scale_color_manual(values = c("2" = "pink", "1" = "blue")) + 
  geom_smooth(method = lm, 
              se = FALSE) + 
  xlab("Depression") +
  ylab("Efficacy")


grid.arrange(eff.anx, eff.dep, ncol=2, top = "Impact of Anxiety and Depression on Efficacy by Sex")
```

```{r, fig.width=8, fig.height=6}
cyn.qnx <- ggplot(df, aes(x = anxiety, y = burnout_cynicism_z, color = sex)) + geom_point() + 
  scale_color_manual(values = c("2" = "pink", "1" = "blue")) + 
  geom_smooth(method = lm, 
              se = FALSE) + 
  xlab("Anxiety") +
  ylab("Cynicism")

cyn.dep <- ggplot(df, aes(x = depression, y = burnout_cynicism_z, color = sex)) + geom_point() + 
  scale_color_manual(values = c("2" = "pink", "1" = "blue")) + 
  geom_smooth(method = lm, 
              se = FALSE) + 
  xlab("Depression") +
  ylab("Cynicism")


grid.arrange(cyn.qnx, cyn.dep, ncol=2, top = "Impact of Anxiety and Depression on Cynicism by Sex")
```

```{r, fig.width=8, fig.height=6}
exh.qnx <- ggplot(df, aes(x = anxiety, y = burnout_exhaustion_z, color = sex)) + geom_point() + 
  scale_color_manual(values = c("2" = "pink", "1" = "blue")) + 
  geom_smooth(method = lm, 
              se = FALSE) + 
  xlab("Anxiety") +
  ylab("Exhaustion")

exh.dep <- ggplot(df, aes(x = depression, y = burnout_exhaustion_z, color = sex)) + geom_point() + 
  scale_color_manual(values = c("2" = "pink", "1" = "blue")) + 
  geom_smooth(method = lm, 
              se = FALSE) + 
  xlab("Depression") +
  ylab("Exhaustion")

grid.arrange(exh.qnx, exh.dep, ncol=2, top = "Impact of Anxiety and Depression on Exhaustion by Sex")
```

```{r, fig.width=8, fig.height=6}
total_burnout.qnx <- ggplot(df, aes(x = anxiety, y = burnout_efficacy_rev_z + burnout_cynicism_z + burnout_exhaustion_z, color = sex)) + geom_point() + 
  scale_color_manual(values = c("2" = "pink", "1" = "blue")) + 
  geom_smooth(method = lm, 
              se = FALSE) + 
  xlab("Anxiety") +
  ylab("Total Burnout")

total_burnout.dep <- ggplot(df, aes(x = depression, y = burnout_efficacy_rev_z + burnout_cynicism_z + burnout_exhaustion_z, color = sex)) + geom_point() + 
  scale_color_manual(values = c("2" = "pink", "1" = "blue")) + 
  geom_smooth(method = lm, 
              se = FALSE) + 
  xlab("Depression") +
  ylab("Total Burnout")


grid.arrange(total_burnout.qnx, total_burnout.dep, ncol=2, top = "Impact of Anxiety and Depression on Total Burnout by Sex")
```

### Impact of year on burnout

```{r, fig.width=6, fig.height=5}
summary_df_efficacy <- df %>%
  group_by(year) %>%
  summarise(
    mean    = mean(burnout_efficacy_rev_z),
    se      = sd(burnout_efficacy_rev_z) / sqrt(n()),
    lower   = mean - qt(0.975, df = n() - 1) * se,
    upper   = mean + qt(0.975, df = n() - 1) * se
  )

ggplot(summary_df_efficacy, aes(x = year, y = mean)) +
  geom_line() +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  labs(
    x = "Years of Study",
    y = "Mean Efficacy",
    title = "Mean Burnout Efficacy by Year with 95% CI"
  ) +
  theme_minimal()
```

```{r, fig.width=6, fig.height=5}
summary_df_cynicism <- df %>%
  group_by(year) %>%
  summarise(
    mean    = mean(burnout_cynicism_z),
    se      = sd(burnout_cynicism_z) / sqrt(n()),
    lower   = mean - qt(0.975, df = n() - 1) * se,
    upper   = mean + qt(0.975, df = n() - 1) * se
  )

ggplot(summary_df_cynicism, aes(x = year, y = mean)) +
  geom_line() +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  labs(
    x = "Years of Study",
    y = "Mean Cynicism",
    title = "Mean Burnout Cynicism by Year with 95% CI"
  ) +
  theme_minimal()
```

```{r, fig.width=6, fig.height=5}
summary_df_exhaustion <- df %>%
  group_by(year) %>%
  summarise(
    mean    = mean(burnout_exhaustion_z),
    se      = sd(burnout_exhaustion_z) / sqrt(n()),
    lower   = mean - qt(0.975, df = n() - 1) * se,
    upper   = mean + qt(0.975, df = n() - 1) * se
  )

ggplot(summary_df_exhaustion, aes(x = year, y = mean)) +
  geom_line() +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  labs(
    x = "Years of Study",
    y = "Mean Exhaustion",
    title = "Mean Burnout Exhaustion by Year with 95% CI"
  ) +
  theme_minimal()
```

```{r, fig.width=6, fig.height=5}
summary_df_total_burnout <- df %>%
  group_by(year) %>%
  summarise(
    mean    = mean(burnout_efficacy_rev_z + burnout_cynicism_z + burnout_exhaustion_z),
    se      = sd(burnout_efficacy_rev_z + burnout_cynicism_z + burnout_exhaustion_z) / sqrt(n()),
    lower   = mean - qt(0.975, df = n() - 1) * se,
    upper   = mean + qt(0.975, df = n() - 1) * se
  )

ggplot(summary_df_total_burnout, aes(x = year, y = mean)) +
  geom_line() +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  labs(
    x = "Years of Study",
    y = "Mean Total Burnout",
    title = "Mean Total Burnout by Year with 95% CI"
  ) +
  theme_minimal()
```

## Partnership Influence over Mental Health

```{r, fig.width=6}
df$part<-as.factor(df$part)

ggplot(df, aes(x = health, fill = part)) +
  geom_density(alpha=0.7)+
  labs(title='Health by Partership')+
  scale_fill_discrete(labels=c('alone', 'partner'))
```


```{r}
ggplot(df, aes(x = burnout_efficacy_rev_z + burnout_cynicism_z + burnout_exhaustion_z, fill = part)) +
  geom_density(alpha=0.7)+
  labs(title='Total Burnout by Partership')+
  scale_fill_discrete(labels=c('alone', 'partner'))
```


```{r}
ggplot(df, aes(x = anxiety, fill = part)) +
  geom_density(alpha=0.7)+
  labs(title='Anxiety by Partership')+
  scale_fill_discrete(labels=c('alone', 'partner'))
```

```{r}
df$sex <- as.numeric(as.character(df$sex))
df$part <- as.numeric(as.character(df$part))
```


## Constructing subsets for each burnout score

```{r}
df_features <- subset(df, select = c(age, year, sex, glang, part, job,
                                       stud_h, health, psyt, job_satisfaction,
                                       cog_empathy, aff_empathy,
                                       academic_motivation,empathy_mean,
                                       depression, anxiety))

df_exhaustion <- cbind(df_features, burnout_exhaustion_z = df$burnout_exhaustion_z)
df_cynicism <- cbind(df_features, burnout_cynicism_z = df$burnout_cynicism_z)
df_efficacy <- cbind(df_features, burnout_efficacy_rev_z = df$burnout_efficacy_rev_z)
df_all_burnout <- cbind(df_features, burnout_total = df$burnout_exhaustion_z + df$burnout_cynicism_z + df$burnout_efficacy_rev_z)
```

## Fitting Random Forest for each target variable

```{r, fig.width=8, fig.height=5}
# Fit Random Forest regression model
set.seed(123)
rf_exhaustion <- randomForest(
  burnout_exhaustion_z ~ ., 
  data = df_exhaustion,
  importance = TRUE,
  ntree = 500
)

# Print model summary
print(rf_exhaustion)

# Plot variable importance
varImpPlot(rf_exhaustion, type = 1, main = "Random Forest Variable Importance - Exhaustion (MSE Increase)")
```


```{r}
# Extract and rank variable importance
ex_importance_df <- importance(rf_exhaustion, type = 1)  # %IncMSE
ex_importance_df <- data.frame(Variable = rownames(ex_importance_df), IncMSE = ex_importance_df[, 1])
ex_importance_df <- ex_importance_df[order(-ex_importance_df$IncMSE), ]
```

```{r, fig.width=8, fig.height=6}
# Set up 5-fold cross-validation (faster than repeatedcv)
cv_ctrl <- trainControl(method = "cv", number = 5)

# Prepare variable importance ordering
all_vars <- ex_importance_df$Variable
ex_cv_results <- data.frame(Num_Variables = 1:length(all_vars), MSPE = NA)

# Loop over 1 to total number of features
for (k in 1:length(all_vars)) {
  selected_vars <- all_vars[1:k]
  formula_k <- as.formula(paste("burnout_exhaustion_z ~", paste(selected_vars, collapse = " + ")))

  # Limit mtry values to avoid warnings and ensure valid tuning
  mtry_max <- max(1, min(5, k))  # Try mtry = 1 up to 5 or k, whichever is smaller
  tune_grid <- expand.grid(mtry = 1:mtry_max)

  # Train model with cross-validation and tuned mtry
  set.seed(123)
  rf_cv_model <- train(
    formula_k,
    data = df_exhaustion,
    method = "rf",
    trControl = cv_ctrl,
    tuneGrid = tune_grid,
    ntree = 100
  )

  # Store best cross-validated MSPE (RMSE^2)
  ex_cv_results$MSPE[k] <- min(rf_cv_model$results$RMSE)^2
}

# Find optimal number of features
ex_opt_k <- which.min(ex_cv_results$MSPE)
ex_opt_mspe <- ex_cv_results$MSPE[ex_opt_k]

cat("Optimal K:", ex_opt_k, "\n")
cat("Optimal MSPE:", round(ex_opt_mspe, 4), "\n")

ggplot(ex_cv_results, aes(x = Num_Variables, y = MSPE)) +
  geom_line(color = "steelblue", linewidth = 1.2) +
  geom_point(color = "red", size = 2) +
  geom_vline(xintercept = ex_opt_k, linetype = "dashed", color = "darkgreen") +
  geom_text(data = data.frame(x = ex_opt_k, y = ex_opt_mspe + 0.01),
            aes(x = x, y = y, label = paste0("Optimal = ", ex_opt_k)),
            inherit.aes = FALSE,
            color = "darkgreen", fontface = "bold", vjust = 0) +
  labs(
    title = "MSPE vs. Number of Top Variables (Burnout-Exhaustion Random Forest, 5-fold CV)",
    x = "Number of Top Variables",
    y = "Mean Squared Prediction Error (CV)"
  ) +
  theme_minimal()

```


```{r, fig.width=8, fig.height=5}
# Fit Random Forest regression model
set.seed(123)
rf_cynicism <- randomForest(
  burnout_cynicism_z ~ ., 
  data = df_cynicism,
  importance = TRUE,
  ntree = 500
)

# Print model summary
print(rf_cynicism)

# Plot variable importance
varImpPlot(rf_cynicism, type = 1, main = "Random Forest Variable Importance - Cynicism (MSE Increase)")
```

```{r}
# Extract and rank variable importance
cy_importance_df <- importance(rf_cynicism, type = 1)  # %IncMSE
cy_importance_df <- data.frame(Variable = rownames(cy_importance_df), IncMSE = cy_importance_df[, 1])
cy_importance_df <- cy_importance_df[order(-cy_importance_df$IncMSE), ]

# Show top predictors
cy_importance_df  # Top 10 for review
```

```{r, fig.width=8, fig.height=6}
library(caret)
library(randomForest)
library(ggplot2)

# Set up 5-fold cross-validation
cv_ctrl <- trainControl(method = "cv", number = 5)

# Prepare importance-ordered variable list
all_vars <- cy_importance_df$Variable
cy_cv_results <- data.frame(Num_Variables = 1:length(all_vars), MSPE = NA)

# Loop through 1 to number of predictors
for (k in 1:length(all_vars)) {
  selected_vars <- all_vars[1:k]
  formula_k <- as.formula(paste("burnout_cynicism_z ~", paste(selected_vars, collapse = " + ")))

  # Safe mtry grid (max 5 or k, whichever is smaller)
  mtry_max <- max(1, min(5, k))
  tune_grid <- expand.grid(mtry = 1:mtry_max)

  # Train with CV
  set.seed(123)
  rf_cv_model <- train(
    formula_k,
    data = df_cynicism,
    method = "rf",
    trControl = cv_ctrl,
    tuneGrid = tune_grid,
    ntree = 100
  )

  # Save best MSPE
  cy_cv_results$MSPE[k] <- min(rf_cv_model$results$RMSE)^2
}

# Find optimal K and MSPE
cy_opt_k <- which.min(cy_cv_results$MSPE)
cy_opt_mspe <- cy_cv_results$MSPE[cy_opt_k]

cat("Optimal K:", cy_opt_k, "\n")
cat("Optimal MSPE:", round(cy_opt_mspe, 4), "\n")

ggplot(cy_cv_results, aes(x = Num_Variables, y = MSPE)) +
  geom_line(color = "steelblue", size = 1.2) +
  geom_point(color = "red", size = 2) +
  geom_vline(xintercept = cy_opt_k, linetype = "dashed", color = "darkgreen") +
  geom_text(data = data.frame(x = cy_opt_k, y = cy_opt_mspe + 0.01),
            aes(x = x, y = y, label = paste0("Optimal = ", cy_opt_k)),
            inherit.aes = FALSE,
            color = "darkgreen", fontface = "bold", vjust = -3.5) +
  labs(
    title = "MSPE vs. Number of Top Variables (Burnout-Cynicism Random Forest, 5-fold CV)",
    x = "Number of Top Variables",
    y = "Mean Squared Prediction Error (CV)"
  ) +
  theme_minimal()
```


```{r, fig.width=8, fig.height=5}
# Fit Random Forest regression model
set.seed(123)
rf_efficacy <- randomForest(
  burnout_efficacy_rev_z ~ ., 
  data = df_efficacy,
  importance = TRUE,
  ntree = 500
)

# Print model summary
print(rf_efficacy)

# Plot variable importance
varImpPlot(rf_efficacy, type = 1, main = "Random Forest Variable Importance - Efficacy (MSE Increase)")
```

```{r}
# Extract and rank variable importance
ea_importance_df <- importance(rf_efficacy, type = 1)  # %IncMSE
ea_importance_df <- data.frame(Variable = rownames(ea_importance_df), IncMSE = ea_importance_df[, 1])
ea_importance_df <- ea_importance_df[order(-ea_importance_df$IncMSE), ]

# Show top predictors
ea_importance_df  # Top 10 for review
```


```{r, fig.width=8, fig.height=6}
# Set up 5-fold cross-validation
cv_ctrl <- trainControl(method = "cv", number = 5)

# Get top variables ranked by importance
all_vars <- ea_importance_df$Variable
ea_cv_results <- data.frame(Num_Variables = 1:length(all_vars), MSPE = NA)

# Loop through 1 to number of top variables
for (k in 1:length(all_vars)) {
  selected_vars <- all_vars[1:k]
  formula_k <- as.formula(paste("burnout_efficacy_rev_z ~", paste(selected_vars, collapse = " + ")))

  # Safe tuning grid
  mtry_max <- max(1, min(5, k))
  tune_grid <- expand.grid(mtry = 1:mtry_max)

  # Train the model with CV and tuned mtry
  set.seed(123)
  rf_cv_model <- train(
    formula_k,
    data = df_efficacy,
    method = "rf",
    trControl = cv_ctrl,
    tuneGrid = tune_grid,
    ntree = 100
  )

  # Store the best MSPE (RMSE squared)
  ea_cv_results$MSPE[k] <- min(rf_cv_model$results$RMSE)^2
}

# Find optimal number of features
ea_opt_k <- which.min(ea_cv_results$MSPE)
ea_opt_mspe <- ea_cv_results$MSPE[ea_opt_k]

cat("Optimal K:", ea_opt_k, "\n")
cat("Optimal MSPE:", round(ea_opt_mspe, 4), "\n")

ggplot(ea_cv_results, aes(x = Num_Variables, y = MSPE)) +
  geom_line(color = "steelblue", size = 1.2) +
  geom_point(color = "red", size = 2) +
  geom_vline(xintercept = ea_opt_k, linetype = "dashed", color = "darkgreen") +
  geom_text(data = data.frame(x = ea_opt_k, y = ea_opt_mspe + 0.01),
            aes(x = x, y = y, label = paste0("Optimal = ", ea_opt_k)),
            inherit.aes = FALSE,
            color = "darkgreen", fontface = "bold", vjust = -1.5) +
  labs(
    title = "MSPE vs. Number of Top Variables (Burnout-Efficacy Random Forest, 5-fold CV)",
    x = "Number of Top Variables",
    y = "Mean Squared Prediction Error (CV)"
  ) +
  theme_minimal()

```

```{r, fig.width=8, fig.height=5}
# Fit Random Forest regression model
set.seed(123)
rf_total_burnout <- randomForest(
  burnout_total ~ ., 
  data = df_all_burnout,
  importance = TRUE,
  ntree = 500
)

# Print model summary
print(rf_total_burnout)

# Plot variable importance
varImpPlot(rf_total_burnout, type = 1, main = "Random Forest Variable Importance - Total Burnout (MSE Increase)")
```

```{r}
# Extract and rank variable importance
total_importance_df <- importance(rf_total_burnout, type = 1)  # %IncMSE
total_importance_df <- data.frame(Variable = rownames(total_importance_df), IncMSE = total_importance_df[, 1])
total_importance_df <- total_importance_df[order(-total_importance_df$IncMSE), ]

# Show top predictors
total_importance_df  # Top 10 for review
```

```{r, fig.width=8, fig.height=6}
# 5-fold cross-validation setup
cv_ctrl <- trainControl(method = "cv", number = 5)

# Ranked variables by importance
all_vars <- total_importance_df$Variable
total_cv_results <- data.frame(Num_Variables = 1:length(all_vars), MSPE = NA)

# Loop over 1 to number of variables
for (k in 1:length(all_vars)) {
  selected_vars <- all_vars[1:k]
  formula_k <- as.formula(paste("burnout_total ~", paste(selected_vars, collapse = " + ")))

  # Valid mtry tuning grid
  mtry_max <- max(1, min(5, k))
  tune_grid <- expand.grid(mtry = 1:mtry_max)

  # Train with CV and tuned mtry
  set.seed(123)
  rf_cv_model <- train(
    formula_k,
    data = df_all_burnout,
    method = "rf",
    trControl = cv_ctrl,
    tuneGrid = tune_grid,
    ntree = 100
  )

  # Save best MSPE (squared RMSE)
  total_cv_results$MSPE[k] <- min(rf_cv_model$results$RMSE)^2
}

# Identify optimal number of variables
total_opt_k <- which.min(total_cv_results$MSPE)
total_opt_mspe <- total_cv_results$MSPE[total_opt_k]

cat("Optimal K:", total_opt_k, "\n")
cat("Optimal MSPE:", round(total_opt_mspe, 4), "\n")

ggplot(total_cv_results, aes(x = Num_Variables, y = MSPE)) +
  geom_line(color = "steelblue", size = 1.2) +
  geom_point(color = "red", size = 2) +
  geom_vline(xintercept = total_opt_k, linetype = "dashed", color = "darkgreen") +
  geom_text(data = data.frame(x = total_opt_k, y = total_opt_mspe + 0.05),
            aes(x = x, y = y, label = paste0("Optimal = ", total_opt_k)),
            inherit.aes = FALSE,
            color = "darkgreen", fontface = "bold", vjust = 0) +
  labs(
    title = "MSPE vs. Number of Top Variables (Total Burnout Random Forest, 5-fold CV)",
    x = "Number of Top Variables",
    y = "Mean Squared Prediction Error (CV)"
  ) +
  theme_minimal()

```

```{r, fig.width=8, fig.height=6}
ex_cv_results$model <- "Exhaustion"
cy_cv_results$model <- "Cynicism"
ea_cv_results$model <- "Efficacy"
total_cv_results$model <- "Total-Burnout"

combined_cv_df <- bind_rows(
  ex_cv_results,
  cy_cv_results,
  ea_cv_results,
  total_cv_results
)

optima_df <- data.frame(
  model = c("Exhaustion", "Cynicism", "Efficacy", "Total-Burnout"),
  x = c(ex_opt_k, cy_opt_k, ea_opt_k, total_opt_k),
  y = c(ex_cv_results$MSPE[ex_opt_k],
        cy_cv_results$MSPE[cy_opt_k],
        ea_cv_results$MSPE[ea_opt_k],
        total_cv_results$MSPE[total_opt_k])
)

combined_cv_df

```
```{r}
optima_df
```

```{r}
ggplot(combined_cv_df, aes(x = Num_Variables, y = MSPE, color = model)) +
  geom_line(size = 1.2) +
  geom_point(size = 2) +

  # Add optimal vertical lines per model
  geom_vline(data = optima_df, aes(xintercept = x, color = model), linetype = "dashed", show.legend = FALSE) +

  # Annotate optimal k values
  geom_text(
    data = optima_df,
    aes(x = x, y = y + 0.2, label = paste0("Optimal = ", x)),
    color = 'black',
    inherit.aes = FALSE,
    fontface = "bold",
    size = 3.5,
    vjust = -2.5
  ) +

  labs(
    title = "MSPE vs. Number of Top Variables\n(All Burnout Random Forest Models, 5-fold CV)",
    x = "Number of Top Variables",
    y = "Mean Squared Prediction Error (CV)",
    color = "Model"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
    axis.text.y = element_text(size = 12),
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    plot.title = element_text(size = 18, face = "bold"),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12)
  )
```


```{r}
ex_importance_df$model = "RF-Exhaustion"
cy_importance_df$model = "RF-Cynicism"
ea_importance_df$model = "RF-Efficacy"
total_importance_df$model = "RF-Total-Burnout"

combined_importance_df <- bind_rows(ex_importance_df, cy_importance_df, ea_importance_df, total_importance_df)
```

```{r}
print(top_n(ex_importance_df, 5, IncMSE)["Variable"])
print(top_n(cy_importance_df, 5, IncMSE)["Variable"])
print(top_n(ea_importance_df, 5, IncMSE)["Variable"])
print(top_n(total_importance_df, 5, IncMSE)["Variable"])
```


```{r}
top_vars <- combined_importance_df %>%
  group_by(model) %>%
  top_n(5, IncMSE) %>%
  ungroup() %>%
  distinct(Variable)

filtered_df <- combined_importance_df %>%
  filter(Variable %in% top_vars$Variable)

completed_df <- filtered_df %>%
  complete(model, Variable, fill = list(IncMSE = 0))

ggplot(completed_df, aes(x = reorder(Variable, IncMSE), y = IncMSE, fill = model)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +
  labs(
    title = "Top 5 Variable Importance per Model",
    x = "Variable",
    y = "Importance (% Increase in MSE)"
  ) +
  theme_minimal() +
  scale_fill_brewer(palette = "Set1") +
  theme(
      axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
      axis.text.y = element_text(size = 12),
      axis.title.x = element_text(size = 14),
      axis.title.y = element_text(size = 14),
      plot.title = element_text(size = 18, face = "bold"),
      plot.subtitle = element_text(size = 14),
      legend.title = element_text(size = 14),
      legend.text = element_text(size = 12)
    )

```


## Feature Importance Plot for Random Forests

```{r, fig.width=8, fig.height=10}
ggplot(combined_importance_df, aes(x = reorder(Variable, IncMSE), y = IncMSE, fill = model)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +
  labs(title = "Variable Importance by Model",
       x = "Variable",
       y = "Importance (% Increase in MSE)") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set1")
```

## Plotting MSPE

```{r}
mspe_summary_df <- data.frame(
  Model = rep(c("Exhaustion", "Cynicism", "Efficacy", "Total Burnout"), each = 2),
  Version = rep(c("Full", "Optimal"), times = 4),
  MSPE = c(
    ex_cv_results$MSPE[length(ex_cv_results$MSPE)], ex_cv_results$MSPE[ex_opt_k],
    cy_cv_results$MSPE[length(cy_cv_results$MSPE)], cy_cv_results$MSPE[cy_opt_k],
    ea_cv_results$MSPE[length(ea_cv_results$MSPE)], ea_cv_results$MSPE[ea_opt_k],
    total_cv_results$MSPE[length(total_cv_results$MSPE)], total_cv_results$MSPE[total_opt_k]
  ),
  Optimal_K = c(NA, ex_opt_k, NA, cy_opt_k, NA, ea_opt_k, NA, total_opt_k)
)

mspe_summary_df$Label <- paste0(mspe_summary_df$Model, "(", mspe_summary_df$Version, ")")
mspe_summary_df
```


```{r, fig.width=8, fig.height=8}

ggplot(mspe_summary_df, aes(x = Label, y = MSPE, color = Model)) +
  geom_point(size = 4) +

  # Annotate MSPE above each point
  geom_text(aes(label = round(MSPE, 2)), 
            vjust = -1, size = 4.5, color = "black") +

  # Annotate K for Optimal models below
  geom_text(
    data = subset(mspe_summary_df, Version == "Optimal"),
    aes(label = paste0("K = ", Optimal_K)),
    vjust = 2, size = 4.5, color = "black", fontface = "italic"
  ) +

  # Annotate K = 16 for Full models below
  geom_text(
    data = subset(mspe_summary_df, Version == "Full"),
    aes(label = "K = 16"),
    vjust = 2, size = 4.5, color = "black", fontface = "italic"
  ) +

  labs(
    title = "MSPE for Full vs Optimal Random Forest Models",
    subtitle = "Each model appears twice (Full and Optimal).",
    x = "Model Version",
    y = "Mean Squared Prediction Error"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
    axis.text.y = element_text(size = 12),
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12)
  )

```

